---
output:
  html_document:
    theme: spacelab
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

`DESeq2` example
==================

[DESeq2](http://bioconductor.org/packages/DESeq2) is one of the most commonly used packages for performing differential expression analysis. It has been for a while on the top 5% of downloaded Bioconductor packages. The [vignette](https://bioconductor.org/packages/release/bioc/vignettes/DESeq2/inst/doc/DESeq2.pdf) explains how to run a `DESeq2` analysis and describes in further detail the example data that we are going to use here. 

This example will show you how to use `regionReport` to make interactive HTML reports from `DESeq2` results. It will also cover how to create a PDF report.

# Input data

First we need to load the example data from the [pasilla](http://bioconductor.org/packages/pasilla) package. Once we have loaded the data, we need to create a _DESeqDataSet_ object and then perform the differential expression analysis using the `DESeq()` function.

```{r 'loadData'}
## Load example data from pasilla package
library('pasilla')
library('DESeq2')

## Get the necessary data from the pasilla package
data('pasillaGenes')
countData <- counts(pasillaGenes)
colData <- pData(pasillaGenes)[, c('condition', 'type')]

## Create DESeqDataSet object from the pasilla package
dds <- DESeqDataSetFromMatrix(countData = countData,
    colData = colData,
    design = ~ condition)

## Perform the differential expression analysis
dds <- DESeq(dds)
```

# HTML report

Once we have the input data we can use the `DESeq2Report()` function from [regionReport](http://bioconductor.org/packages/regionReport). First we create a directory where we'll have the data.

```{r 'createOutputDir'}
## The output will be saved in the 'DiffBind-example' directory
dir.create('DESeq2-example', showWarnings = FALSE, recursive = TRUE)
```

Next, we can create the HTML report. In this case we'll change the default theme by using the `theme_bw()` function from the [ggplot2](https://cran.r-project.org/web/packages/ggplot2/index.html) package.

```{r 'createReport'}
## Use ggplot2::theme_bw()
library('ggplot2')

library('regionReport')
## Create the HTML report
report <- DESeq2Report(dds, project = 'HTML report',
    intgroup = c('condition', 'type'), outdir = 'DESeq2-example',
    output = 'index', theme = theme_bw())
```


You can view the final HTML report at [DESeq2-example](/regionReportSupp/DESeq2-example/index.html).

# PDF report

The HTML report has an interactive table with the top features (in this case genes). It allows you to re-order these top features by different criteria or even search for your feature of interest. However, sometimes you might prefer to create a PDF report. The following code will allow you to create such a report.

```{r 'createReportPDF', eval = FALSE}
## Create PDF version of the same report
report <- DESeq2Report(dds, project = 'PDF report', 
    intgroup = c('condition', 'type'), outdir = 'DESeq2-example',
    output = 'DESeq2Report', theme = theme_bw(), output_format = 'pdf_document',
    device = 'pdf')
```


```{r 'createReportRealPDF', echo = FALSE, results = 'hide'}
## Generate the HTML report in a clean environment
library('devtools')

cat("## Generate the report in an isolated environment
## This helps avoid https://github.com/rstudio/rmarkdown/issues/248

## Load example data from pasilla package
library('pasilla')
library('DESeq2')

## Create DESeqDataSet object from the pasilla package
data('pasillaGenes')
countData <- counts(pasillaGenes)
colData <- pData(pasillaGenes)[, c('condition', 'type')]

dds <- DESeqDataSetFromMatrix(countData = countData,
    colData = colData,
    design = ~ condition)
dds <- DESeq(dds)

## Use ggplot2::theme_bw()
library('ggplot2')

## Create PDF version of the same report
library('regionReport')
report <- DESeq2Report(dds, project = 'PDF report', 
    intgroup = c('condition', 'type'), outdir = 'DESeq2-example',
    output = 'DESeq2Report', theme = theme_bw(), output_format = 'pdf_document',
    device = 'pdf')

", file = 'DESeq2-report-isolated-PDF.R')
clean_source('DESeq2-report-isolated-PDF.R', quiet=TRUE)
file.remove('DESeq2-report-isolated-PDF.R')
```

You can view the final PDF report at [DESeq2-example PDF](/regionReportSupp/DESeq2-example/DESeq2Report.pdf).

# Reproducibility

```{r 'reproducibility'}
## Date generated:
Sys.time()

## Time spent making this page:
proc.time()

## R and packages info:
options(width = 120)
devtools::session_info()
```

