---
output:
  html_document:
    theme: spacelab
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

`regionReport` supplementary website
====================================

This is the supplementary website for the `regionReport` paper. 

# Example use cases

## `bumphunter` case

An example using [bumphunter](http://bioconductor.org/packages/release/bioc/html/bumphunter.html) is showcased at [bumphunter.html](http://www.bioconductor.org/packages/devel/bioc/vignettes/regionReport/inst/doc/bumphunterExample.html). This file shows the code for obtaining a set of simulated differentially methylated regions and creating a HTML report using `renderReport()`. The report is a bit simpler than the one in the example of `renderReport()` because there is no p-value variable. The output report from this example is available at [bumphunter-example](http://www.bioconductor.org/packages/devel/bioc/vignettes/regionReport/inst/doc/bumphunterExampleOutput.html).


## `DiffBind` case

An example using [DiffBind](http://bioconductor.org/packages/release/bioc/html/DiffBind.html) is showcased at [DiffBind.html](/regionReportSupp/DiffBind.html). This file shows the code for obtaining a set of differentially bounded sites and creating a HTML report using `renderReport()` with custom code to create a MA plot and two PCA plots. The output report from this example is available at [DiffBind-example](/regionReportSupp/DiffBind-example/index.html).

## `derfinder` cases

This section uses three different data sets as described in the `derfinder` paper ([bioRxiv preprint](http://biorxiv.org/content/early/2015/02/19/015370)).

The three reports can be viewed following these links:

* [brainspan](/regionReportSupp/brainspan/basicExploration.html)
* [hippo](/regionReportSupp/hippo/basicExploration.html)
* [simulation](/regionReportSupp/simulation/basicExploration.html)

Note that each report is around 40-50 MB in size and can take some time to load.

The code used for generating these reports is available at the `derfinder` paper ([bioRxiv preprint](http://biorxiv.org/content/early/2015/02/19/015370)) supplementary website [derSoftware](http://lcolladotor.github.io/regionReportSupp/).


# Installation

Get R 3.2.x from [CRAN](http://cran.r-project.org/) as well as pandoc 
1.12.3 or newer from [here](http://johnmacfarlane.net/pandoc/installing.html). Note that at the time of writing this page, some of the functionality of `regionReport` is only available at Bioconductor-devel (BioC version 3.2), which is why you need R 3.2.x.

Once you have the correct version of R, you can install `regionReport` directly from _Bioconductor_ by using:

```{r 'install', eval = FALSE}
## Install regionReport
source('http://bioconductor.org/biocLite.R')
## Verify that you get a message saying (or with newer versions):
# Bioconductor version 3.2 (BiocInstaller 1.19.6), ?biocLite for help
## If the message says that you are using Bioconductor version 3.1 try using
# useDevel()
biocLite('regionReport')
```

That command should install all the dependencies for using `regionReport`. This package does suggest a couple other ones, which you might not need to use. If you wish to install them use:


```{r 'installSuggested', eval = FALSE}
## Other suggested packages by regionReport
source('http://bioconductor.org/biocLite.R')
biocLite(c('biovizBase', 'Cairo', 'TxDb.Hsapiens.UCSC.hg19.knownGene'))
```


Note that for the latest `knitrBootstrap` templates you will have to use:

```{r 'installKnitrBootstrap', eval = FALSE}
## Install latest knitrBootstrap from GitHub
library('devtools')
install_github('jimhester/knitrBootstrap')
```

Some of the examples require other packages, in which case you would need to install the following packages.

```{r 'installExamples', eval = FALSE}
## Bumphunter example
source("http://bioconductor.org/biocLite.R")
biocLite(c('bumphunter', 'GenomicRanges', 'biovizBase'))

## DiffBind example
source("http://bioconductor.org/biocLite.R")
biocLite(c('DiffBind', 'biovizBase', 'TxDb.Hsapiens.UCSC.hg19.knownGene',
    'bumphunter'))

## derfinder examples. Should be installed after biocLite('regionReport')
source("http://bioconductor.org/biocLite.R")
biocLite('derfinder')
```



# Miscellaneous

[genomicRanges.R](/regionReportSupp/genomicRanges.R) has simple code for determining how many unique packages depend, import or suggest `GenomicRanges`.

This page was last updated at `r Sys.time()`.
