---
output:
  html_document:
    theme: spacelab
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

`regionReport` supplementary website
====================================

This is the supplementary website for the [regionReport](http://bioconductor.org/packages/regionReport) paper available at [F1000Research](http://f1000research.com/articles/4-105/v1). 

# Example use cases

## `DESeq2` case

[regionReport](http://bioconductor.org/packages/regionReport) has a specific template for `DESeq2` results. The file [DESEq2.html](/regionReportSupp/DESeq2.html) shows how to create a HTML and a PDF report using results from `DESeq2`. The resulting HTML report is available at [DESeq2-example](/regionReportSupp/DESeq2-example/index.html) and the PDF version at [DESeq2REport](/regionReportSupp/DESeq2-example/DESEq2Report.pdf).

## `bumphunter` case

An example using [bumphunter](http://bioconductor.org/packages/bumphunter) is showcased at [bumphunter.html](http://www.bioconductor.org/packages/devel/bioc/vignettes/regionReport/inst/doc/bumphunterExample.html). This file shows the code for obtaining a set of simulated differentially methylated regions and creating a HTML report using `renderReport()`. The report is a bit simpler than the one in the example of `renderReport()` because there is no p-value variable. The output report from this example is available at [bumphunter-example](http://www.bioconductor.org/packages/devel/bioc/vignettes/regionReport/inst/doc/bumphunterExampleOutput.html).


## `DiffBind` case

An example using [DiffBind](http://bioconductor.org/packages/DiffBind) is showcased at [DiffBind.html](/regionReportSupp/DiffBind.html). This file shows the code for obtaining a set of differentially bounded sites and creating a HTML report using `renderReport()` with custom code to create a MA plot and two PCA plots. This example also shows how to change the distribution plot templates to use histograms instead of density plots. The output report from this example is available at [DiffBind-example](/regionReportSupp/DiffBind-example/index.html) and it uses `rmarkdown` as the engine which since version 0.9.5 allows toggling of code.

## `derfinder` cases

This section uses different data sets as described in the `derfinder` paper ([bioRxiv preprint](http://biorxiv.org/content/early/2015/02/19/015370)).

The reports can be viewed following these links:

* [brainspan](/regionReportSupp/brainspan/basicExploration.html)
* [hippo](/regionReportSupp/hippo/basicExploration.html)

Note that each report is around 40-50 MB in size and can take some time to load. These reports were generated using `knitrBootstrap` as the engine prior to `rmarkdown` v0.9.5.

The code used for generating these reports is available at the supplementary websites [derSupplement](http://leekgroup.github.io/derSupplement/) and [derCountSupp](http://leekgroup.github.io/derCountSupp/).


# Installation

Get R 3.2.x from [CRAN](http://cran.r-project.org/) as well as pandoc 
1.12.3 or newer from [here](http://johnmacfarlane.net/pandoc/installing.html). Note that at the time of writing this page, some of the functionality of `regionReport` is only available at Bioconductor-devel (BioC version 3.2), which is why you need R 3.2.x.

Once you have the correct version of R, you can install `regionReport` directly from _Bioconductor_ by using:

```{r 'install', eval = FALSE}
## Install regionReport
source('http://bioconductor.org/biocLite.R')
## Verify that you get a message saying (or with newer versions):
# Bioconductor version 3.2 (BiocInstaller 1.19.6), ?biocLite for help
## If the message says that you are using Bioconductor version 3.1 try using
# useDevel()
biocLite('regionReport')
```

That command should install all the dependencies for using `regionReport`. This package does suggest a couple other ones, which you might not need to use. If you wish to install them use:


```{r 'installSuggested', eval = FALSE}
## Other suggested packages by regionReport
source('http://bioconductor.org/biocLite.R')
biocLite(c('biovizBase', 'Cairo', 'TxDb.Hsapiens.UCSC.hg19.knownGene'))
```


Note that for the latest `knitrBootstrap` templates you will have to use:

```{r 'installKnitrBootstrap', eval = FALSE}
## Install latest knitrBootstrap from GitHub
library('devtools')
install_github('jimhester/knitrBootstrap')
```

Some of the examples require other packages, in which case you would need to install the following packages.

```{r 'installExamples', eval = FALSE}
## DESeq2 example
source("http://bioconductor.org/biocLite.R")
biocLite('pasilla')

## Bumphunter example
source("http://bioconductor.org/biocLite.R")
biocLite(c('bumphunter', 'GenomicRanges', 'biovizBase'))

## DiffBind example
source("http://bioconductor.org/biocLite.R")
biocLite(c('DiffBind', 'biovizBase', 'TxDb.Hsapiens.UCSC.hg19.knownGene',
    'bumphunter'))

## derfinder examples. Should be installed after biocLite('regionReport')
source("http://bioconductor.org/biocLite.R")
biocLite('derfinder')
```



# Miscellaneous

[genomicRanges.R](/regionReportSupp/genomicRanges.R) has simple code for determining how many unique packages depend, import or suggest `GenomicRanges`.

This page was last updated at `r Sys.time()`.
